metric-learn: Metric Learning Algorithms in Python

### 2020-06-20 metric-learn-jmlr.tex
minted option to allow arXiv submission
add picture and gitignore
first modifications

\usepackage{jmlr2e}
\usepackage{minted}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{stmaryrd}
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\aurelien}[1]{\todo[inline,caption={},color=orange!40]{{\it Aurelien:~}#1}}
\newcommand{\william}[1]{\todo[inline,caption={},color=blue!40]{{\it William:~}#1}}
%\renewcommand{\aurelien}[1]{}
%\renewcommand{\william}[1]{}

@@

% \aurelien{we could put the presentation of metric learning and supervision as Sec 2, and put the implemented algorithms in the overview of the package section as Section 3}

\section{Background on Metric Learning} \label{metriclearning}

@@

% use t to put figure on top (preferred) Thanks ! 
\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.25\textwidth} % "0.45" donne ici la largeur de l'image
        \centering \includegraphics[scale=0.45]{labels.pdf}
        \caption{class supervision}\label{fig:full}
    \end{subfigure}
    \begin{subfigure}[t]{0.25\textwidth}
        \centering \includegraphics[scale=0.45]{pairs.pdf}
        \caption{pair supervision}\label{fig:pairs}
    \end{subfigure}
    \begin{subfigure}[t]{0.40\textwidth}
        \centering \includegraphics[scale=0.45]{quadruplets.pdf}
        \caption{quadruplet supervision}\label{fig:quadruplets}
    \end{subfigure}
    \caption{Different types of supervision for metric learning %(\subref{fig:full}) Class supervision: make samples from the same label (here, identity) closer together than samples from different labels. (\subref{fig:pairs}) Pair supervision: make similar pairs (here, corresponding to the same person) to be closer than dissimilar pairs (different persons). (\subref{fig:quadruplets}) Quadruplet supervision: make leftmost pairs (here, people of similar age) closer than rightmost pairs (of bigger age difference).
    illustrated on face image data taken from the Labeled Faces in the Wild dataset \citep{Huang12}.}\label{fig:flowers}
\end{figure}

@@

%\aurelien{Fig caption is redundant with the main text. could reduce it.}

\section{Overview of the Package}

@@

Currently, \texttt{metric-learn} implements 9 popular metric learning algorithms.
Supervised learners include Neighborhood Components Analysis \citep[NCA,][]{Goldberger04}, Large Margin Nearest Neighbors \citep[LMNN,][]{Weinberger09}, Relative Components Analysis \citep[RCA,][]{Shental02},\footnote{RCA takes as input slightly weaker supervision in the form of \emph{chunklets} (groups of points of same class).} Local Fisher Discriminant Analysis \citep[LFDA,][]{Sugiyama07} and Metric Learning for Kernel Regression \citep[MLKR,][]{Weinberger07}.
The latter is designed for regression problems with continuous labels.
Pair learners include Mahalanobis Metric for Clustering \citep[MMC,][]{Xing2002a}, Information Theoretic Metric Learning \citep[ITML,][]{Davis07} and Sparse High-Dimensional Metric Learning \citep[SDML,][]{Qi09}.
The package implements one quadruplet learner: Metric Learning from Relative Comparisons by Minimizing Squared Residual \citep[LSML,][]{Liu12}.
Detailed descriptions of these algorithms can be found in the package documentation.

>>>>

\usepackage{jmlr2e}
\usepackage[cachedir=.,finalizecache]{minted}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{stmaryrd}
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\aurelien}[1]{\todo[inline,caption={},color=orange!40]{{\it Aurelien:~}#1}}
\newcommand{\william}[1]{\todo[inline,caption={},color=blue!40]{{\it William:~}#1}}
%\renewcommand{\aurelien}[1]{}
%\renewcommand{\william}[1]{}

@@

% \aurelien{we could put the presentation of metric learning and supervision as Sec 2, and put the implemented algorithms in the overview of the package section as Section 3}
Other packages for metric-learning already exist, however, they have a different focus: \textit{pyDML} only contains supervised metric learning algorithms, and \textit{pytorch-metric-learning} is focused on deep metric learning, with the pytorch framework. 
\tod[inline]{Talk about the matlab package}
\section{Background on Metric Learning} \label{metriclearning}

@@

% use t to put figure on top (preferred) Thanks ! 
\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.25\textwidth} % "0.45" donne ici la largeur de l'image
        \centering \includegraphics[scale=0.45]{labels.pdf}
        \caption{class supervision}\label{fig:full}
    \end{subfigure}
    \begin{subfigure}[t]{0.25\textwidth}
        \centering \includegraphics[scale=0.45]{pairs.pdf}
        \caption{pair supervision}\label{fig:pairs}
    \end{subfigure}
    \begin{subfigure}[t]{0.40\textwidth}
        \centering \includegraphics[scale=0.45]{triplets.pdf}
	\caption{triplet supervision}\label{fig:triplets}
    \end{subfigure}
    \begin{subfigure}[t]{0.40\textwidth}
        \centering \includegraphics[scale=0.45]{quadruplets.pdf}
        \caption{quadruplet supervision}\label{fig:quadruplets}
    \end{subfigure}
    \caption{Different types of supervision for metric learning %(\subref{fig:full}) Class supervision: make samples from the same label (here, identity) closer together than samples from different labels. (\subref{fig:pairs}) Pair supervision: make similar pairs (here, corresponding to the same person) to be closer than dissimilar pairs (different persons). (\subref{fig:quadruplets}) Quadruplet supervision: make leftmost pairs (here, people of similar age) closer than rightmost pairs (of bigger age difference).
    illustrated on face image data taken from the Labeled Faces in the Wild dataset \citep{Huang12}.}\label{fig:flowers}
\end{figure}

@@

%\aurelien{Fig caption is redundant with the main text. could reduce it.}
\section{Overview of the Package}

@@

Currently, \texttt{metric-learn} implements 9 popular metric learning algorithms.
Supervised learners include Neighborhood Components Analysis \citep[NCA,][]{Goldberger04}, Large Margin Nearest Neighbors \citep[LMNN,][]{Weinberger09}, Relative Components Analysis \citep[RCA,][]{Shental02},\footnote{RCA takes as input slightly weaker supervision in the form of \emph{chunklets} (groups of points of same class).} Local Fisher Discriminant Analysis \citep[LFDA,][]{Sugiyama07} and Metric Learning for Kernel Regression \citep[MLKR,][]{Weinberger07}.
The latter is designed for regression problems with continuous labels.
Pair learners include Mahalanobis Metric for Clustering \citep[MMC,][]{Xing2002a}, Information Theoretic Metric Learning \citep[ITML,][]{Davis07} and Sparse High-Dimensional Metric Learning \citep[SDML,][]{Qi09}.
The package implements one quadruplet learner: Metric Learning from Relative Comparisons by Minimizing Squared Residual \citep[LSML,][]{Liu12}, and one triplet learner: Sparse Compositional Metric Learning \citep[SCML,][]{Shi15}.
Detailed descriptions of these algorithms can be found in the package documentation.
